Abstract Plots

### 2021-07-29 Abstract.Rmd
Created dataframe for all signatures with certain dilutions.

@@

### Sensitivity/MMR

```{r}
AVG.sens.MMR <- vector(mode = "list", length =length(step))

for (iteration in 1:50){
  sens.MMR <- performance(test.MMR, measure = "sens")

  for(ind in 1:length(sens.MMR@x.values)){
    thresh = as.vector(slot(sens.MMR, "x.values")[[ind]])
    sens = as.vector(slot(sens.MMR, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.sens.MMR[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (sens[high.ind] - sens[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.sens.MMR[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + sens[low.ind]
      }
    }
    else{
      AVG.sens.MMR[[ind]][iteration] = NA
    }
  }
}

sens.MMR.vec = c()
for (avg in 1:length(AVG.sens.MMR)){
  sens.MMR.vec[avg] = mean(AVG.sens.MMR[[avg]], na.rm = TRUE)
}
```

### Sensitivity/Tobacco

```{r}
AVG.sens.tob <- vector(mode = "list", length = length(step))

for(iteration in 1:50){
  sens.tob <- performance(test.tob, measure = "sens")

  for(ind in 1:length(sens.tob@x.values)){
    thresh = as.vector(slot(sens.tob, "x.values")[[ind]])
    sens = as.vector(slot(sens.tob, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.sens.tob[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (sens[high.ind] - sens[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.sens.tob[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + sens[low.ind]
      }
    }
    else{
      AVG.sens.tob[[ind]][iteration] = NA
    }
  }
}

sens.tob.vec = c()
for (avg in 1:length(AVG.sens.tob)){
  sens.tob.vec[avg] = mean(AVG.sens.tob[[avg]], na.rm = TRUE)
}
```

### Sensitivity across signatures

```{r}
sensitivity = append(sens.MMR.vec, sens.tob.vec)
signature.sens = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(sens.tob.vec)))
dilution = append(step/10, step/10)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

@@

### Specificity/MMR

```{r}
AVG.spec.MMR <- vector(mode = "list", length = length(step))

for(iteration in 1:50){
  spec.MMR <- performance(test.MMR, measure = "spec")

  for(ind in 1:length(spec.MMR@x.values)){
    thresh = as.vector(slot(spec.MMR, "x.values")[[ind]])
    spec = as.vector(slot(spec.MMR, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.spec.MMR[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (spec[high.ind] - spec[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.spec.MMR[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + spec[low.ind]
      }
    }
    else{
      AVG.spec.MMR[[ind]][iteration] = NA
    }
  }
}

spec.MMR.vec = c()
for (avg in 1:length(AVG.spec.MMR)){
  spec.MMR.vec[avg] = mean(AVG.spec.MMR[[avg]], na.rm = TRUE)
}
```

### Specificity/Tobacco

```{r}
AVG.spec.tob <- vector(mode = "list", length = length(step))

for (iteration in 1:50){
  spec.tob <- performance(test.tob, measure = "spec")

  for(ind in 1:length(spec.tob@x.values)){
    thresh = as.vector(slot(spec.tob, "x.values")[[ind]])
    spec = as.vector(slot(spec.tob, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.spec.tob[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (spec[high.ind] - spec[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.spec.tob[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + spec[low.ind]
      }
    }
    else{
      AVG.spec.tob[[ind]][iteration] = NA
    }
  }
}

spec.tob.vec = c()
for (avg in 1:length(AVG.spec.tob)){
  spec.tob.vec[avg] = mean(AVG.spec.tob[[avg]], na.rm = TRUE)
}
```

### Specificity across all signatures

```{r}
specificity = append(spec.MMR.vec, spec.tob.vec)
signature.spec = append(rep("MMR", length(sens.MMR.vec)),
                        rep("Tobacco", length(spec.tob.vec)))
dilution = append(step/10, step/10)
spec.df <- data.frame(dilution, specificity, signature.spec)

@@

@@

```{r}
step = seq(50, 1000, by = 50)
MMR.probabilities <- vector(mode = "list", length = length(step))
MMR.truth <- vector(mode = "list", length = length(step))

@@

```{r}
step = seq(50, 1000, by = 50)
tob.probabilities <- vector(mode = "list", length = length(step))
tob.truth <- vector(mode = "list", length = length(step))

@@

```{r}
AVG.sens.MMR <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  sens.MMR <- performance(load.MMR, measure = "sens")

  for(ind in 1:length(sens.MMR@x.values)){
    thresh = as.vector(slot(sens.MMR, "x.values")[[ind]])
    sens = as.vector(slot(sens.MMR, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.sens.MMR[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (sens[high.ind] - sens[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.sens.MMR[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + sens[low.ind]
      }
    }
    else{
      AVG.sens.MMR[[ind]][iteration] = NA
    }
  }
}

load.sens.MMR.vec = c()
for (avg in 1:length(AVG.sens.MMR)){
  load.sens.MMR.vec[avg] = mean(AVG.sens.MMR[[avg]], na.rm = TRUE)
}
```

```{r}
AVG.sens.tob <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  sens.tob <- performance(load.tob, measure = "sens")

  for(ind in 1:length(sens.tob@x.values)){
    thresh = as.vector(slot(sens.tob, "x.values")[[ind]])
    sens = as.vector(slot(sens.tob, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.sens.tob[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (sens[high.ind] - sens[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.sens.tob[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + sens[low.ind]
      }
    }
    else{
      AVG.sens.tob[[ind]][iteration] = NA
    }
  }
}

load.sens.tob.vec = c()
for (avg in 1:length(AVG.sens.tob)){
  load.sens.tob.vec[avg] = mean(AVG.sens.tob[[avg]], na.rm = TRUE)
}
```

@@

```{r}
AVG.spec.MMR <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  spec.MMR <- performance(load.MMR, measure = "spec")

  for(ind in 1:length(spec.MMR@x.values)){
    thresh = as.vector(slot(spec.MMR, "x.values")[[ind]])
    spec = as.vector(slot(spec.MMR, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.spec.MMR[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (spec[high.ind] - spec[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.spec.MMR[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + spec[low.ind]
      }
    }
    else{
      AVG.spec.MMR[[ind]][iteration] = NA
    }
  }
}

load.spec.MMR.vec = c()
for (avg in 1:length(AVG.spec.MMR)){
  load.spec.MMR.vec[avg] = mean(AVG.spec.MMR[[avg]], na.rm = TRUE)
}
```

```{r}
AVG.spec.tob <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  spec.tob <- performance(load.tob, measure = "spec")

  for(ind in 1:length(spec.tob@x.values)){
    thresh = as.vector(slot(spec.tob, "x.values")[[ind]])
    spec = as.vector(slot(spec.tob, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.spec.tob[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (spec[high.ind] - spec[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.spec.tob[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + spec[low.ind]
      }
    }
    else{
      AVG.spec.tob[[ind]][iteration] = NA
    }
  }
}

load.spec.tob.vec = c()
for (avg in 1:length(AVG.spec.tob)){
  load.spec.tob.vec[avg] = mean(AVG.spec.tob[[avg]], na.rm = TRUE)
}
```

>>>>

```{r}
evaluate_perf <- function(num_iter, length, pred_obj, perf_method){
  AVG.sens <- vector(mode = "list", length = length)

  for (iteration in 1:num_iter){
  sens.obj <- performance(pred_obj, measure = perf_method)

  for(ind in 1:length(sens.obj@x.values)){
    thresh = as.vector(slot(sens.obj, "x.values")[[ind]])
    sens = as.vector(slot(sens.obj, "y.values")[[ind]])
    if (length(thresh) > 2){
      if (identical(which(thresh<=0.5), integer(0))){
        AVG.sens[[ind]][iteration] = NA
      }
      else{
        low.ind = max(which(thresh >=0.5))
        high.ind = min(which(thresh <=0.5))
        #point slop formula of a line
        slope = (sens[high.ind] - sens[low.ind]) / (thresh[high.ind] - thresh[low.ind])
        AVG.sens[[ind]][iteration] = slope*(0.5 - thresh[low.ind]) + sens[low.ind]
      }
    }
    else{
      AVG.sens[[ind]][iteration] = NA
        }
      }
    }

  sens.vec = c()
  for (avg in 1:length(AVG.sens)){
    sens.vec[avg] = mean(AVG.sens[[avg]], na.rm = TRUE)
  }

  return(sens.vec)
}
```

@@

```{r}
sens.MMR.vec = evaluate_perf(100, length(step), test.MMR, "sens")
```

```{r}
sens.tob.vec = evaluate_perf(100, length(step), test.tob, "sens")
```

### Sensitivity plot

```{r}
sensitivity = append(sens.MMR.vec, sens.tob.vec)
signature.sens = append(rep("Signature 6", length(sens.MMR.vec)),
                        rep("Signature 4", length(sens.tob.vec)))
dilution = append(step/10, step/10)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

@@

```{r}
spec.MMR.vec = evaluate_perf(100, length(step), test.MMR, "spec")
spec.tob.vec = evaluate_perf(100, length(step), test.tob, "spec")
```

### Specificity plot

```{r}
specificity = append(spec.MMR.vec, spec.tob.vec)
signature.spec = append(rep("Signature 6", length(sens.MMR.vec)),
                        rep("Signature 4", length(spec.tob.vec)))
dilution = append(step/10, step/10)
spec.df <- data.frame(dilution, specificity, signature.spec)

@@

## File of all signatures diluted with FFPE noise

```{r}
#columns in data frame
sens = vector(mode = "list", length = length(signature.names))
spec = vector(mode = "list", length = length(signature.names))
signature = vector(mode = "list", length = length(signature.names))

#create data frame values 10 times
iteration.num = 3
for (iteration in 1:iteration.num){
  #iterate through each signature
  for (sig.num in 1:length(signature.names)){
    #store name of signature (once for every dilution)
    signature[[sig.num]] = append(signature[[sig.num]],
                                  rep(signature.names[sig.num], 5))
    #store values generated by get_classification_df for each dilution
    probabilities <- vector(mode = "list", length = 5)
    truth <- vector(mode = "list", length = 5)
    #initialize accumulator
    i = 1
      #each signature is diluted with 10%, 30%, 50%, 70%, and 90% FFPE noise
      # (1000 mutations total each time)
      for (x in c(100, 300, 500, 700, 900)){
        #create some percent of FFPE noise
        sample.ffpe <- create_signature_sample_vector(ffpe.signature, x)
        ffpe.truth <- rep("FFPE", x)
        #fill the rest with true signal
        sample <- create_signature_sample_vector(signature.matrix.list[[sig.num]], 1000-x)
        sample.truth <- rep(signature.names[sig.num], 1000-x)
        #evaluate using Bayes
        test <- get_classification_df(list(sample, sample.ffpe), 
                                      c(signature.names[sig.num],"FFPE"),
                                      list(signature.matrix.list[[sig.num]],
                                           ffpe.signature))
        #truth column turned into binary for ROCR package
        classification <- test %>%
          mutate(trueBinary = ifelse(truth == signature.names[sig.num],1,0))
        #store probabilities and truths for particular dilution
        probabilities[[i]] <- classification[[3]]
        truth[[i]] <- classification$trueBinary
        i = i + 1
      }
    #evaluate all 5 dilution samples
    pred = prediction(probabilities, truth)
    sens[[sig.num]] = append(sens[[sig.num]], evaluate_perf(100, 5, pred, "sens"))
    spec[[sig.num]] = append(spec[[sig.num]], evaluate_perf(100, 5, pred, "spec"))
  }
}

#vector indicating dilution amount
percent.FFPE = rep(c("10%", "30%", "50%", "70%", "90%"),
                   length(signature.names)*iteration.num)
#vectorize lists
signature = unlist(signature)
sens = unlist(sens)
spec = unlist(spec)

#convert into data frame
table = data.frame(percent.FFPE, signature, sens, spec)

#avg the multiple sensitivity/specificity values for each dilution and each signature
table <- table %>%
  group_by(percent.FFPE, signature) %>%
  summarize(sens = mean(sens, na.rm = TRUE),
            spec = mean(spec, na.rm = TRUE))
```

@@

```{r}
step_load = seq(50, 1000, by = 50)
MMR.probabilities <- vector(mode = "list", length = length(step))
MMR.truth <- vector(mode = "list", length = length(step))

@@

```{r}
tob.probabilities <- vector(mode = "list", length = length(step))
tob.truth <- vector(mode = "list", length = length(step))

@@

```{r}
load.sens.MMR.vec = evaluate_perf(100, length(step_load), load.MMR, "sens")
load.sens.tob.vec = evaluate_perf(100, length(step_load), load.tob, "sens")
```

@@

```{r}
load.spec.MMR.vec = evaluate_perf(100, length(step.load), load.MMR, "spec")
load.spec.tob.vec = evaluate_perf(100, length(step.load), load.tob, "spec")
```
